Predicting The Outcome T1 and Gen G Games Based on Leads

### 2024-04-19 paper/paper.qmd
updated bitex file and added it to pdf

League of Legends is one of the most popular video games in 2024 and has held that stature for the last decade.[CITE TWITCH STATS] It is an extremely nuanced game but a brief overview shall be provided here but it will be explained with more depth in the @sec-dis.  The game consists of 2 teams of 5 players each, in which both teams compete to destroy the enemy 'nexus.' The map is split into 3 lanes and a 'jungle' which is a dark area in between each of the lanes. While the primary objective of the game is simple, that is, to destroy the enemy nexus, there are a variety of strategies that players can implore to do it. For instance, one team may spend the majority of its time maximizing its gold income in order to buy items that make them stronger and once this is done, it will be easier to kill the enemy players and destroy the enemy nexus. Another popular strategy would be to sacrifice your own gold income to deny the enemy gold income as well as experience. While the gold may be even, you will have more experience points and will be stronger with higher levels. This strength disparity once again can allow you to kill your opponents easier and yup, you guessed it, destroy the enemy nexus.

@@

The data used in this paper was downloaded directly fromt the Riot Games API, the company that owns league of legends. This is available to everyone for free(although an account must be created.) When a game of league of legends is played online, a large amount of data is recorded and stored in their database. These can then be accessed using their API, which allows this data to be queried. The data used in this paper comes from games played by each of the players on the pro teams, and were within the last 2 years. This allows it to be more indicative of their current performance, rather than their performance from 2016. It is taken from their solo queue games, which is essentially the regular games that anyone can play online by themselves and not the professional games in which all of the team's players team up and play against another full team. (As the name suggests, solo queue means you are queueing for a game alone.)

@@

A logistic regression model works by instead of considering an error value, which is done in linear regression, it considers a distribution for each of the inputs. The variability of these distributions inherently create the variability of the outcome which is associated to the error value we get in linear regression. The main advantage to this comes from the assumption made in linear regression models in which the error value is assumed to cancel out with each other(forming a normal distribution) In this case, consider the input of the cs at 10 minutes. In some games the players get more than their average and some games less, but they generally follow a normal distribution. The error is included by the variance of this normal. Assuming both of the inputs to follow a normal distribution makes sense because the number of games is high and this is the general trend of the data. (CITE FIGURE)

>>>>

League of Legends is one of the most popular video games in 2024 and has held that stature for the last decade.It has over 100 million active users every month[@citeleague] and is an extremely nuanced game but a brief overview shall be provided here but it will be explained with more depth in the @sec-dis.  The game consists of 2 teams of 5 players each, in which both teams compete to destroy the enemy 'nexus.' The map is split into 3 lanes and a 'jungle' which is a dark area in between each of the lanes. While the primary objective of the game is simple, that is, to destroy the enemy nexus, there are a variety of strategies that players can implore to do it. For instance, one team may spend the majority of its time maximizing its gold income in order to buy items that make them stronger and once this is done, it will be easier to kill the enemy players and destroy the enemy nexus. Another popular strategy would be to sacrifice your own gold income to deny the enemy gold income as well as experience. While the gold may be even, you will have more experience points and will be stronger with higher levels. This strength disparity once again can allow you to kill your opponents easier and yup, you guessed it, destroy the enemy nexus.

@@

The data used in this paper was downloaded directly fromt the Riot Games API [@riotAPI], the company that owns league of legends. This is available to everyone for free(although an account must be created.) When a game of league of legends is played online, a large amount of data is recorded and stored in their database. These can then be accessed using their API, which allows this data to be queried. The data used in this paper comes from games played by each of the players on the pro teams, and were within the last 2 years. This allows it to be more indicative of their current performance, rather than their performance from 2016. It is taken from their solo queue games, which is essentially the regular games that anyone can play online by themselves and not the professional games in which all of the team's players team up and play against another full team. (As the name suggests, solo queue means you are queueing for a game alone.)

@@

A logistic regression model works by instead of considering an error value, which is done in linear regression, it considers a distribution for each of the inputs. The variability of these distributions inherently create the variability of the outcome which is associated to the error value we get in linear regression. The main advantage to this comes from the assumption made in linear regression models in which the error value is assumed to cancel out with each other(forming a normal distribution) In this case, consider the input of the cs at 10 minutes. In some games the players get more than their average and some games less, but they generally follow a normal distribution. The error is included by the variance of this normal. Assuming both of the inputs to follow a normal distribution makes sense because the number of games is high and this is the general trend of the data(see @fig-t1level)
